### 2020-02-26 Thesis-Chapter-Background.tex
Work on intro/background

>>>>

Private use of encryption has a contentious history. [Some highlights.]

Electronic encryption must be understood as a technological development embedded in the longer history of privacy and
human rights. [This is where I'd like to understand more of the legal side. With a historical perspective.]

Privacy is not encryption's only purpose, however. Encryption is the technical foundation for many forms of computer and
network security. [Properties: confidentiality, authentication, integrity, non-repudiation; primitives: hashed
passwords, digital signatures, ...; technologies: PKI, TLS, SSO/Kerberos, VPNs, disk encryption, blockchains (might get
eye-rolls).]

Electronic encryption's dual role as enabler of perfect privacy and cornerstone of computer security may be the central
conflict in the exceptional access debate. Those who focus on its role in privacy object to its absolute power. Those
who focus on its role in security rely on its absolute power.

% Encryption requires absolute cryptographic fidelity in order to provide security.

### 2020-02-26 Thesis-Chapter-Intro.tex
Work on intro/background

\begin{itemize}
    \item In the pursuit of data privacy, legislative action is part of the threat model
\end{itemize}

@@

\begin{itemize}
    \item The lack of convincing of legislative bodies and law enforcement agencies demands that the technical community continue the discussion
    \item The ability to access digital data is important and will be increasingly important for investigations
    \item Various forms of encryption are foundational all elements of online security
    \item Mass surveillance is a grave danger that representative governments are not immune from
    \item International and human rights considerations significantly constrain workable solutions
    \item Transparency to data access is critical for public trust
\end{itemize}

>>>>

\begin{itemize}
    \item In the pursuit of data privacy, legislative action is part of the threat model
    \item Legislative action is a highly likely
    \item We as the technical community need to be prepared
\end{itemize}

@@

\begin{itemize}
    \item The failure to convince legislative bodies and law enforcement agencies demands that the technical community continue the discussion
    \item The ability to access digital data is important and will be increasingly important for investigations
    \item Various forms of encryption are foundational all elements of online security
    \item Mass surveillance is a grave danger that representative governments are not immune from
    \item International and human rights considerations significantly constrain workable solutions
    \item Transparency to data access is critical for public trust
\end{itemize}
